Enforcing idempotency in neural networks

### 2024-12-02 paper.tex
Abstract and title

\title{Title of the paper}

@@

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch (3~picas) on
  both the left- and right-hand margins. Use 10~point type, with a vertical
  spacing (leading) of 11~points.  The word \textbf{Abstract} must be centered,
  bold, and in point size 12. Two line spaces precede the abstract. The abstract
  must be limited to one paragraph.
\end{abstract}

>>>>

\title{Enforcing idempotency in neural networks}

@@

\begin{abstract}
  In this work we propose a new architecture-agnostic method for training idempotent neural networks. An idempotent operator satisfies $f(x) = f(f(x))$, meaning it can be applied iteratively with no effect beyond the first application. Neural networks used in image generation, sorting algorithms, data compression, and many other areas represent non-linear idempotent projections. Using methods from perturbation theory and linear algebra, we derive the recurrence relation ${w' \leftarrow 3w^2 + 2w^3}$ and show that in the linear case it has 1) idempotent fixed points, and 2) is attracting around idempotent points. Additionally, we provide experimental results for the non-linear case showing more than 10x idempotent error improvement over the canonical gradient-based approach. Finally, we demonstrate scalability as we train a generative network successfully using only a simple reconstruction loss paired with our method. As a gradient-free optimisation strategy for a non-convex optimisation problem we believe the ideas presented here could be applied more broadly beyond idempotent neural networks.
\end{abstract}
